Jilbert's Distinction Centrality

### 2025-03-01 index.qmd
do it

```{r}
#| tbl-cap: "Distinction Centrality Scores of Nodes in the Star Graph (Normalized)."
   tab.cent(distinction(g1, norm = TRUE)[, 1:4])
```

@@

```{r}
#| tbl-cap: "Distinction Centrality Scores of Nodes in the Structural Fold (Normalized)."
   tab.cent(distinction(g2, norm = TRUE)[, 1:4])
```

>>>>

```{r}
#| tbl-cap: "Distinction Centrality Scores of Nodes in the Star Graph (Normalized)."
   tab.cent(distinction(g1, scale = TRUE)[, 1:4])
```

@@

```{r}
#| tbl-cap: "Distinction Centrality Scores of Nodes in the Structural Fold (Normalized)."
   tab.cent(distinction(g2, scale = TRUE)[, 1:4])
```
